---
title: "Online Appendix (OA) Tables"
author: " "
date: " "
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

```{r include=FALSE}
library(readxl)
library(DT)
library(tidyverse)
library(reactable)
```

```{r include=FALSE}
T1 <- read_excel("data/Combined Tables.xlsx", sheet = "MS Table 1")
OA_T1 <- read_excel("data/Combined Tables.xlsx", sheet = "OA Table 1")
OA_T2 <- read_excel("data/Combined Tables.xlsx", sheet = "OA Table 2")
OA_T3 <- read_excel("data/Combined Tables.xlsx", sheet = "OA Table 3")
```

<!-- `reactable` vignette -->
<!-- https://glin.github.io/reactable/index.html -->

To access supporting files (e.g., static tables, supplementary analyses), please click [here](https://osf.io/uz8qd/?view_only=06c93751e7894b97a001cce87a082b82).

<br>

### Online Appendix (OA) Table 1    
*Overview of Definitions and Measures of Respect in Leadership*    
```{r echo=FALSE, message=FALSE, warning=FALSE}
OA_T1 %>%
  select(-Index) %>%
  reactable(.,
          resizable=TRUE,
          filterable=TRUE,
          searchable=TRUE,
          bordered = TRUE,
          highlight = TRUE,
          strip= TRUE,
          wrap = FALSE,
          fullWidth = TRUE,
          compact=FALSE,
          showSortable=TRUE,
          columns = list(
            `Citation` = colDef(name = "Citation", width = 400),
            `Theoretical Tradition` = colDef(name = "Theoretical Tradition", width = 400),
            `Respect in Leadership Construct` = colDef(name = "Respect in Leadership Construct", width = 400),
            `Definition/Description of Respectful in Leadership` = colDef(name = "Definition/Description of Respectful in Leadership", width = 1000),
            `Measure Used` = colDef(name = "Measure Used", width = 400)
            )
          )
```

### Online Appendix (OA) Table 2  
*Overview of Research Designs, Samples, and Key Findings of Studies on Respect in Leadership*  
```{r echo=FALSE, message=FALSE, warning=FALSE}
OA_T2$`2019 Impact Factor`<-as.numeric(OA_T2$`2019 Impact Factor`)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
OA_T2 %>%
  select(-Index) %>%
  reactable(.,
          resizable=TRUE,
          filterable=TRUE,
          searchable=TRUE,
          bordered = TRUE,
          highlight = TRUE,
          strip= TRUE,
          wrap = FALSE,
          fullWidth = TRUE,
          compact=FALSE,
          showSortable=TRUE,
          columns = list(
            `Citation` = colDef(name = "Citation", width = 400),
            `Journal` = colDef(name = "Journal", width = 400),
            `2019 Impact Factor` = colDef(name = "2019 Impact Factor", width = 150, format = colFormat(digits = 2)),
            `Research Design` = colDef(name = "Research Design", width = 400),
            `Theoretical Tradition` = colDef(name = "Theoretical Tradition", width = 250)
            )
          )
```

### Online Appendix (OA) Table 3  
*Overview of Measures of Respect in Leadership*  

```{r echo=FALSE, message=FALSE, warning=FALSE}
OA_T3 %>%
  select(-Index) %>%
  reactable(.,
          resizable=TRUE,
          filterable=TRUE,
          searchable=TRUE,
          bordered = TRUE,
          highlight = TRUE,
          strip= TRUE,
          wrap = FALSE,
          fullWidth = TRUE,
          compact=FALSE,
          showSortable=TRUE
          ,
          columns = list(
            `Theoretical Tradition` = colDef(name = "Theoretical Tradition", width = 400),
            `Source` = colDef(name = "Source", width = 200),
            `Short Citation` = colDef(name = "Short Citation", width = 400),
            `Long Citation` = colDef(name = "Long Citation", width = 200),
            `k` = colDef(name = "k", width = 150, format = colFormat(digits = 1)),
            `Sample Size` = colDef(name = "Sample Size", width = 250),
            `Content Representativeness` = colDef(name = "Content Representativeness", width = 300),
            `Structure` = colDef(name = "Structure", width = 300),
            `Response Process` = colDef(name = "Response Process", width = 300),
            `Predictive/Concurrent/Incremental Validity` = colDef(name = "Predictive/Concurrent/Incremental Validity", width = 400),
            `Convergent/Divergent Validity` = colDef(name = "Convergent/Divergent Validity", width = 300),
            `Feasibility/Practicality` = colDef(name = "Feasibility/Practicality", width = 300)
           )
          )
```